\textsf{Are frontier models superhuman chemists?}

### 2024-03-19 src/tex/appendix.tex
one more author

\subsection{Related work}
Existing benchmarks such as those from \textcite{guo2023large}, \cite{sun2023scieval}, \textcite{Schulze_Balhorn_2024}, \textcite{Cai_2024} fail to comply with most of the requirements stipulated above (see \Cref{tab:existing benchmarks}). 
While these benchmarks could provide useful insights in the short-term, they cannot follow the rapid additions to the \gls{llm} space. 
\chembench aims to correct this through a set of developments: compatibility with BigBench, end-to-end automation, special focus on chemical safety, employment of diverse prompting strategies and specialized notation for molecules and mathematical symbols. 
Moreover, we believe that our robust framework, including the platform \url{chembench.org}, will engage the community in open-source contributions.

@@

\Cref{fig:all_questions_models_completely_correct_radar} shows the performance of the models on the different topics of the \chembench corpus.

@@

\begin{figure}
    \centering
    \includegraphics{figures/performance_per_topic.pdf}
    \caption{Caption}
    \label{fig:performance_per_topic}
    \script{analyze_performance_per_source.py}
\end{figure}

@@

\begin{figure} 
    \centering
    \includegraphics{figures/confidence_score_distributions.pdf}
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.}} 
    \label{fig:confidence_score_distributions}
    \script{plot_confidence_score_distributions.py}
\end{figure}

>>>>

\subsection{Related work}
Existing benchmarks such as those from \textcite{guo2023large}, \cite{sun2023scieval}, \textcite{Schulze_Balhorn_2024}, \textcite{Cai_2024} fail to comply with most of the requirements stipulated above. 
While these benchmarks could provide useful insights in the short-term, they cannot follow the rapid additions to the \gls{llm} space. 
\chembench aims to correct this through a set of developments: compatibility with BigBench, end-to-end automation, special focus on chemical safety, employment of diverse prompting strategies and specialized notation for molecules and mathematical symbols. 
Moreover, we believe that our robust framework, including the platform \url{chembench.org}, will engage the community in open-source contributions.

@@

\Cref{fig:all_questions_models_completely_correct_radar_overall} shows the performance of the models on the different topics of the \chembench corpus.

@@

\begin{figure}
    \centering
    \includegraphics{figures/performance_per_topic.pdf}
    \caption{\textbf{Fraction of completely correctly answered questions per data source.} The heatmap shows, in color, the fraction of questions that were answered completely correctly by the models for each data source. The performance is measured as the fraction of questions that were answered completely correctly by the models. A score of 1 indicates that all questions were answered completely correctly, while a score of 0 indicates that none of the questions were answered completely correctly.}
    \label{fig:performance_per_topic}
    \script{analyze_performance_per_source.py}
\end{figure}

@@

\begin{figure} 
    \centering
    \includegraphics{figures/confidence_score_distributions.pdf}
    \caption{\textbf{Distribution of confidence scores reported by \glspl{llm}.} \Glspl{llm} show different distributions of confidence scores. The confidence scores are reported on an ordinal scale from 1 to 5, with 1 indicating low confidence and 5 indicating high confidence. The barplots show how many questions were answered with each confidence score.}
    \label{fig:confidence_score_distributions}
    \script{plot_confidence_score_distributions.py}
\end{figure}

### 2024-03-19 src/tex/ms.tex
one more author

\begin{figure}
    \centering
    %\includegraphics{figures/chem-bench-completley-correct-calculation-vs-no-calculation.pdf}
    \caption{Caption}
    \label{fig:calculation_performance}
\end{figure}

@@

In \Cref{fig:estimated_difficulty} we show that there is no significant correlation between the estimated difficulty and whether the models answered the question correctly or not.
For applications in which humans might rely on the models to provide answers, this is a concerning observation highlighting the need for critical reasoning in the interpretation of the models' outputs.\autocite{Li_2023}
For example, for the questions about the safety profile of compounds, GPT-4 reported an average confidence of XX (on a scale of 1--5) for the XX (out of XX) questions it answered in correctly (XX for the XX questions it answered correctly).

>>>>

@@

In \Cref{fig:confidence_vs_performance} we show that for some models there is no significant correlation between the estimated difficulty and whether the models answered the question correctly or not.
For applications in which humans might rely on the models to provide answers, this is a concerning observation highlighting the need for critical reasoning in the interpretation of the models' outputs.\autocite{Li_2023}
For example, for the questions about the safety profile of compounds, GPT-4 reported an average confidence of XX (on a scale of 1--5) for the XX (out of XX) questions it answered in correctly (XX for the XX questions it answered correctly).
